Report

### 2020-11-19 report.Rmd
Function to compare the two models

```{r, eval = TRUE}
#https://stackoverflow.com/questions/44457243/regression-tables-in-r-markdown-rmarkdown-html-pdf

model_log_bm_f3y_table <- summary_log_bm_f3y %>%
  filter(model == "mod_bm_quad2") %>%
  filter(variable %in% get_com_str_var(all = FALSE)) %>%
  mutate(
    reg_table = map(model_obj, broom::tidy),
    anova_table = map(anova, broom::tidy)
  )

model_log_bm_f3y_table[["reg_table"]] %>% 
  bind_rows(.) %>%
  mutate(variable = rep(model_log_bm_f3y_table[["variable"]], each = 6)) %>%
  select(variable, everything()) %>%
  kable(.,
    booktabs = TRUE, 
    caption = 
      paste0(
      "Regression table for the model: dN =",
      "bm + dBm + dBm^2 + bm*dBm + bm*dBm^2."
    )) %>% 
  kable_styling(latex_options =c("scale_down")) %>%
  #add_header_above(c(" " = 3, "Indirect effects via" = 5)) %>%
  #column_spec(1:2, width = "3cm") %>%
  collapse_rows(columns = 1, valign = "top")
```

```{r}
bind_rows(model_log_bm_f3y_table[["anova_table"]]) %>% 
  mutate(variable = rep(model_log_bm_f3y_table[["variable"]], each = 6)) %>%
  select(variable, everything()) %>%
  kable(., booktabs = TRUE,
    caption = 
      paste0(
      "ANOVA table for the model: dN =",
      "bm + dBm + dBm^2 + bm*dBm + bm*dBm^2."
    )
  )

```{r}
map_dfr(model_log_bm_f3y_table[["model_obj"]], broom::glance) %>%
  mutate(variable = model_log_bm_f3y_table[["variable"]]) %>%
  select(variable, everything()) %>%
  kable(., booktabs = TRUE,
    caption = 
      paste0(
      "Model summary for the model: dN =",
      "bm + dBm + dBm^2 + bm*dBm + bm*dBm^2."
    )
  )
```

@@

pred_log_bm_quad2_plot <- map2(model_log_bm_f3y$data, pred_log_bm_quad2$pred_df,
  plot_pred_data)
legend_quad2 <- get_legend(pred_log_bm_quad2_plot[[1]])
pred_log_bm_quad2_plot %<>% map(., ~.x + theme(legend.position = "none"))
top <- plot_grid(plotlist = pred_log_bm_quad2_plot, labels = model_log_bm_f3y$variable)
plot_grid(top, legend_quad2, rel_widths = c(1, .1))
```
-

@@

```{r, eval = FALSE}
complete_log_quad2 <- summary_log_bm_f3y_by_protocol %>%
  filter(model == "mod_bm_quad2", protocol_type == "complete") %>%
  mutate(
    reg_table = map(model_obj, broom::tidy),
    anova_table = map(anova, broom::tidy)
  )

complete_log_quad2[["reg_table"]] %>% 
  bind_rows(.) %>%
  mutate(variable = rep(complete_log_quad2[["variable"]], each = 6)) %>%
  select(variable, everything()) %>%
  kable(.,
    booktabs = TRUE, 
    caption = 
      paste0(
      "Regression table for the model: dN =",
      "bm + dBm + dBm^2 + bm*dBm + bm*dBm^2."
    ) 
  )

complete_log_quad2[["anova_table"]] %>% 
  bind_rows(.) %>%
  mutate(variable = rep(complete_log_quad2[["variable"]], each = 6)) %>%
  select(variable, everything()) %>%
  kable(., booktabs = TRUE,
    caption = 
      paste0(
      "ANOVA table for the model: dN =",
      "bm + dBm + dBm^2 + bm*dBm + bm*dBm^2."
    )
  )
```

>>>>

```{r, eval = TRUE}
#https://stackoverflow.com/questions/44457243/regression-tables-in-r-markdown-rmarkdown-html-pdf
model_log_bm_f3y_table <- get_table_from_summary(
  .data = summary_log_bm_f3y,
  model =  "mod_bm_quad2",
  variable = get_com_str_var(all = FALSE)
)

model_log_bm_f3y_table[["reg_table"]] %>% 
  kable(.,
    booktabs = TRUE, 
    caption = 
      paste0(
      "Regression table for the model: dN =",
      "bm + dBm + dBm^2 + bm*dBm + bm*dBm^2."
    )) %>% 
  kable_styling(latex_options =c("scale_down")) %>%
  #add_header_above(c(" " = 3, "Indirect effects via" = 5)) %>%
  #column_spec(1:2, width = "3cm") %>%
  collapse_rows(columns = 1, valign = "top")
```

```{r}
model_log_bm_f3y_table[["anova_table"]] %>% 
  kable(., booktabs = TRUE,
    caption = 
      paste0(
      "ANOVA table for the model: dN =",
      "bm + dBm + dBm^2 + bm*dBm + bm*dBm^2."
    )
  ) %>%
  collapse_rows(columns = 1, valign = "top")
```

```{r}
model_log_bm_f3y_table[["model_obj"]] %>%
  kable(., booktabs = TRUE,
    caption = paste0( "Model summary for the model: dN =",
      "bm + dBm + dBm^2 + bm*dBm + bm*dBm^2.")
  )
```

@@

pred_log_bm_quad2_plot <- map2(model_log_bm_f3y$data, pred_log_bm_quad2$pred_df,
  plot_pred_data)
legend_quad2 <- get_legend(pred_log_bm_quad2_plot[[1]])
pred_log_bm_quad2_plot %<>% map(., ~.x + theme(legend.position = "none"))
top <- plot_grid(plotlist = pred_log_bm_quad2_plot, labels = model_log_bm_f3y$variable)
plot_grid(top, legend_quad2, rel_widths = c(1, .1))
```

### Compare Quad2 and piecewiseregression

```{r}
effect_quad2_piece <- tibble(
  effect = c("Dynamic of biomass", "disassembly/assembly", "com size", "Effect of bm dyn dep on com size?", "Effect of bm dyn dep on disassembly/assembly context?", "Effect of bm dyn dep on both dis/assembly and com size ?"),
  mod_bm_quad2 = c("bm_slope", "I(bm_slope^2)", "bm", "bm_slope:bm", "I(bm_slope^2)", "bm:I(bm_slope^2)"),
  mod_all_bm = c("bm_slope", "inc_fTRUE", "bm", "bm_slope:bm", "bm_slope:inc_fTRUE", "bm_slope:inc_fTRUE:bm")
)

combin <- expand.grid(
  variable = get_com_str_var(),
  mod_bm_quad2 = unique(effect_quad2_piece$mod_bm_quad2), 
  stat = c("estimate", "p.value")
) %>%
left_join(select(effect_quad2_piece, 2:3)) %>%
pivot_longer(cols = c(mod_bm_quad2, mod_all_bm), names_to = "model", values_to = "term") %>%
mutate_all(as.character)

comparison_table <- distinct(combin) %>%
  mutate(
    coeff = pmap_dbl(list(variable, stat, model, term),
      ~get_coef_from_terms(mydata = model_log_bm_f3y,
	variable = ..1, model = ..3, term = ..4, type = ..2
	) 
  )) %>%
arrange(variable)
unique(comparison_table$term)

test <- comparison_table %>%
  left_join(
    pivot_longer(effect_quad2_piece, cols = c(mod_bm_quad2, mod_all_bm),
      names_to = "model", values_to = "term")
  ) %>%
  select(variable:model, coeff, effect) %>%
  pivot_wider(names_from = stat, values_from = coeff) %>%
  pivot_wider(names_from = model, values_from = c(estimate, p.value))

test2 <- comparison_table %>%
  left_join(
    pivot_longer(effect_quad2_piece, cols = c(mod_bm_quad2, mod_all_bm),
      names_to = "model", values_to = "term")) %>%
  filter(stat == "p.value") %>%
  select(variable:model, coeff, effect) %>%
  pivot_wider(names_from = stat, values_from = coeff) %>%
  pivot_wider(names_from = model, values_from = c(p.value)) %>%
  kable(., booktabs = TRUE,
    caption = 
      paste0(
      "Comparison of the two Statistical model"
    )
  ) %>%
  collapse_rows(columns = 1, valign = "top")
```

@@

```{r, eval = FALSE}
complete_log_quad2 <- get_table_from_summary(.data = summary_log_bm_f3y_by_protocol, model = "mod_bm_quad2", protocol = "complete")

complete_log_quad2[["reg_table"]] %>% 
  kable(.,
    booktabs = TRUE, 
    caption = 
      paste0(
      "Regression table for the model: dN =",
      "bm + dBm + dBm^2 + bm*dBm + bm*dBm^2."
    ) 
  )

complete_log_quad2[["anova_table"]] %>% 
  kable(., booktabs = TRUE,
    caption = 
      paste0(
      "ANOVA table for the model: dN =",
      "bm + dBm + dBm^2 + bm*dBm + bm*dBm^2."
    )
  )
```
